\documentclass[12pt,a4paper,titlepage]{report} 
\usepackage{titlesec}
\usepackage{cite}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{calligra}
\usepackage[T1]{fontenc}
\lstset{language=csh, frame=single, basicstyle=\footnotesize}
\usepackage{float} %enables use of [H] placement specifiers in figures 
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{array}
\usepackage[table, x11names]{xcolor}
\usepackage{svg}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{morefloats}
\usepackage{listings}
\usepackage{color}
\renewcommand{\contentsname}{Indholdsfortegnelse}
\renewcommand*\listfigurename{Figures}

\newcommand{\tab}[1]{\hspace{1cm}{#1}}

\titleformat{\chapter}
{\normalfont\LARGE\bfseries}{\thechapter.\ }{10pt}{}
\titlespacing*{\chapter}{0pt}{0pt}{10pt}

\begin{document}
\input{forside.tex}
\begin{abstract}
As humans we wonder about life and death in relation to, if there could be an afterlife. Many ideas about the eschatological events including divine judgment have evolved through the history of Christianity. Still today there has been no unity in the Christian circles about a doctrine concerning how the afterlife will be. However, there is a doctrine concerning the resurrection and this states that Christianity believes that there is an afterlife however it may appear.

The doctrine of double outcome, doctrine of apokatastasis and annihilationism are ideas concerning eschatology and all provide different ideas about the human situation inbetween life, death and afterlife. Since we humans all are going to die at some point, the thoughts about an afterlife and continuance from this life are enticing life opportunities. In this respect an analysis of Augustin, Regin Prenter, Jürgen Moltmann, Gregorory of Nyssa and Barth will present how they imagine the human situation in the light of divine judgment. However these theologians all encounter a point in the imagination of the divine where they have to acknowledge that some things demand ones silence and rely on a hope for atonement.
\end{abstract}
\setcounter{section}{0}
\bibliographystyle{apalike}



\setcounter{tocdepth}{1}
{\small \tableofcontents}

\clearpage

\input{intro.tex}
\input{tese.tex}
\input{kilder.tex}
\input{teori.tex}
\input{eskatologi.tex}
\input{udgang.tex}
\input{apo.tex}
\input{skaersilden.tex}
\input{universalisme.tex}
\input{annihilation.tex}
\input{diskussion.tex}
\input{konklusion.tex}
\input{litliste.tex}
\end{document}